Cannibalism among the supermassive black holes

### 2018-10-10 paper.tex
Updates from ShareLaTeX

\subsection{Merger tree}
Our merger tree data came from two sources:
\begin{itemize}
\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12), which was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.  The data was centered around SMBHs at each redshift slice from $4 > z > 0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
\end{itemize}

@@

The Kulier15 merger tree collected black holes entering galaxies during the simulation and noted the time after z=4 at which they entered their host galaxy.  Nothing further was done with them, so each galaxy had a "running list" of other galaxies/BHs orbiting them at z=0.  Clean up this paragraph.

After finding our subject galaxies, we curve-fit their total masses as a function of time using a $7^{th}$-order polynomial fit, so as to be able to use their masses in the AR-Chain code.  Additionally, we curve-fit each galaxy's accreted+seed central black hole mass to exponential functions of time.

The following cosmological parameters were used in the simulations of both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.

\subsubsection{Galactic Stellar Mass Adjustment}
Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.  Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.  We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range (see Figure \ref{fig:stellar1}).
\begin{figure}[h!]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  X's shown is example of our rescaled stellar masses}
\label{fig:stellar1}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Oriting BHs".png}
\caption{Luminosities of Orbiting BHs at z=0}
\label{fig:loobhs}
\end{center}
\end{figure}

>>>>

\subsection{Merger tree}
Our merger tree data came from two sources, each of which in turn used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}:
\begin{itemize}
\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12).  In this paper, the authors simulated and compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.  For our simulations, we only utilized total stellar mass, without regard for whether the mass was accreted or formed in situ.
\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15).  The data was centered around SMBHs at each redshift slice from $4 > z > 0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
\end{itemize}

@@

The above criteria narrowed the field of eligible galaxies down to 53.

The following cosmological parameters were used in our simulations, consistent with both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.

\subsubsection{Stellar Mass Adjustment}
Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.  Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.  We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range (see Figure \ref{fig:stellar1}).
\begin{figure}[h!]
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  X's shown is example of our rescaled stellar masses}
\label{fig:stellar1}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Oriting BHs".png}
\caption{Luminosities of Orbiting BHs at z=0}
\label{fig:loobhs}
\end{center}
\end{figure}
